\begin{document}

\section{Refining Neural Network}

In this section, we will be talking about how the neural network goes through change to score best.

\subsection{Initial Draft}

For this neural network, we will firstly start off with the following code. A simple neural network, with 2 layers, the input, and the output.

\begin{lstlisting}[language=Python]

def model_c():
    
    model = keras.models.Sequential()
    model.add(keras.layers.Dense(<neurons>, input_shape=(12,), \
		kernel_initializer='normal', activation='relu'))
    model.add(keras.layers.Dense(1, kernel_initializer='normal'))
    model.compile(loss='mean_squared_error', optimizer='adam')
   
    return model

\end{lstlisting}

\paragraph{input\_shape} This defines how many dimensions we have the input as, we have 12 parameters, hence 12.

\paragraph{kernal\_initializer} This defines how the weights are randomly allocated before the learning process. For this we just use the normal.

\paragraph{activation} We will simply be using \textbf{ReLU} (rectified linear unit) as our activation function. This simply maps any positive values in the neuron to a linear function, anything non-positive is mapped to 0.

\paragraph{loss} The loss describes how far the machine is predicting all values correctly. In this case, we will use mean\_squared\_error as our minimum loss target as we are dealing with a \textit{regression} problem.

\paragraph{optimizer} It's hard to describe what is \textbf{Adam} (adaptive moment estimation), however, it is described to be "better" than \textbf{SGD} (Stochastic Gradient Descent). More info here: https://machinelearningmastery.com/adam-optimization-algorithm-for-deep-learning/

\subsubsection{Layer Improvements}

We will keep it short on the guess and check for neuron layers, here are the results and improvements done.

\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|} 
\hline
\multicolumn{7}{|c|}{Parameters} & \multicolumn{2}{|c|}{Loss} & {} \\
\hline
\# & $L_1$ & $L_2$ & $L_3$ & $L_4$ & Epochs & Batch Size & Mean & STDEV & File Name \\
\hline
1 & 108 & 54 & 27 & {} & 25 & 1 & 1.87 & 0.46 & e25\_104\_52\_26 \\
\hline
\multicolumn{10}{|c|}{Make Layers divisible by input dimensions (12)} \\
\hline
2 & 96 & 48 & 24 & {} & 25 & 1 & 1.96 & 0.40 & e25\_96\_48\_24 \\
\hline
\multicolumn{10}{|c|}{Increase Batch Size to 5} \\
\hline
2 & 96 & 48 & 24 & {} & 25 & 5 & 1.83 & 0.43 & e25\_96\_48\_24\_5 \\
\hline
\multicolumn{10}{|c|}{Increase Batch Size to 100} \\
\hline
2 & 96 & 48 & 24 & {} & 25 & 100 & 1.80 & 0.52 & e25\_96\_48\_24\_100 \\
\hline
\end{tabular}	


\end{document}
